Open Data, Open Source and Open Standards in chemistry: \\ The Blue Obelisk five years on

### 2011-05-15 paper.tex
Corrected some of the text on Avogadro and comp. chem.
Also, added some details about the recently split out OpenQube. Whilst
still in a very early stage, I think that it should also be considered a
Blue Obelisk project, and it is being actively worked on and was
incubated by the Avogadro project.

Avogadro has already been mentioned as a GUI for preparing calculations.
It uses Open Babel to read the output of several electronic structure
packages, and also to write the input files for each. Jmol (see below)
can also depict computational chemistry results including molecular orbitals.

>>>>

Avogadro has already been mentioned as a GUI for preparing calculations.
It uses Open Babel to read the output of several electronic structure
packages. Avogadro generates input files on the fly in response to user
input on forms, as well as allowing inline editing of the files before
they are saved to disk. It also features intuitive syntax highlighting
for GAMESS input files, allowing expert users to easily spot mistakes
before saving an input file to disk.

In addition to this, significant development of new parsing routines took
place in an Avogadro plugin to read in basis sets, and electronic structure
output in order to calculate molecular orbital and electron density grids.
This code was written to be parallel, using desktop shared memory parallelism
and high level APIs in order to significantly speed up analysis. Most of this
code was recently separated from the plugin, and released as a BSD licensed
library, that is now used by the latest version of Avogadro, called OpenQube.
Jmol (see below)
can also depict computational chemistry results including molecular orbitals.
